# Análisis Espaciales

```{r librerias}
# Levanto el dataset de la encuesta

library(dplyr)
library(readr)
library(stringr)
library(tidygeocoder)
library(sf)
library(mapview)
library(here)
           
```
```{r}
# Levanto el dataset de la encuesta

df_encuesta <- read_rds(here::here("Outputs", "df_encuesta.rds"))

df_mapa <- df_encuesta |>
select(viv_calle,
       viv_altura,
       viv_partido) |>
mutate(viv_provincia = "Buenos Aires",
       viv_pais = "Argentina",
       viv_calle_ok = if_else(str_starts(viv_calle, "[0-9]"),
                                        str_glue("Calle {viv_calle}"),
                                        viv_calle),
       viv_calle_ok = str_replace(viv_calle_ok, "entre.*$", ""), # Saco los "entre"
       viv_calle_ok = str_replace(viv_calle_ok, "[.][0-9]+$", ""), # Saco los decimales
       street = as.character(str_glue("{viv_altura} {viv_calle_ok}")))

geo <- geo(street = df_mapa$street,
        county = df_mapa$viv_partido,
        state = df_mapa$viv_provincia,
        country = df_mapa$viv_pais,
        method = 'osm',
        lat = latitude , 
        long = longitude,
        full_results = FALSE,
        progress_bar = TRUE)

lat_long <- df_mapa |>
            bind_cols(geo) |>
          write_rds(here("Outputs","lat_long.rds"))

lat_long_sf <- lat_long |>
                  filter(!is.na(latitude)) |>
                  st_as_sf(
         coords = c("longitude", "latitude"),
         crs = 4326,
         dim = "XY") |>
         write_rds(here("Outputs","lat_long_sf.rds"))

mapview(lat_long_sf)
          
```


You can add parts to organize one or more book chapters together. Parts can be inserted at the top of an .Rmd file, before the first-level chapter heading in that same file. 

Add a numbered part: `# (PART) Act one {-}` (followed by `# A chapter`)

Add an unnumbered part: `# (PART\*) Act one {-}` (followed by `# A chapter`)

Add an appendix as a special kind of un-numbered part: `# (APPENDIX) Other stuff {-}` (followed by `# A chapter`). Chapters in an appendix are prepended with letters instead of numbers.



